Bayesian exponential random graph modelling of KWL Burial network

### 2020-04-05 analysis/paper/paper.Rmd
Explore age as additional node attribute, the result doesn't change a lot. Add sentences about chronology

Burials were assigned to pre-European contact period, post-European contact period, and Chinese period based on the stratigraphic data, radiocarbon dates, and diagnostic porcelain such as white-glazed jars as a time indicator of the arrival of the Europeans[citation]. The burials that were disturbed severely due to modern construction are excluded due to incomplete data. Since the accumulation of imported prestige goods in burials is commonly observed, we assign the burials into four classes, high, medium, low, and none, accoutring to the total number of burial goods to indicate the index of wealth.

@@

Based on the quantity and quality of grave goods among burials, we can reconstruct social networks from the distribution of prestige goods, including imported ceramic and beads based on the principle that prestige materials usually relate to social status. We build network where burials represent actors (nodes in the network) linked by sharing the same prestige goods.

We assume burial network represents the relations among people and social structure based on the argument that 
## Bayesian inference for Exponential Random Graph Models

>>>>

Burials were assigned to the pre-European period, European and post-European period, and Chinese period for network comparison. Since the sedimentary characteristics show vertical and lateral continuity cross units of AD section, depth is used as the first criterion for burial chronology. The chronology is then evaluated by the burials with light grey glazed jars, also called An-ping jars produced most likely in China and circulated in Southeast Asia from the late 16th to 18th century but are often found at sites with the European occupation in the early 17th century in Taiwan [@Berrocal2018; @Hsieh1995; @Ketel2011]. In addition to the diagnostic porcelain, three radiocarbon dates of charcoal associated with three different burials are used as another evidence to evaluate the chronology [@Chen2007]. Some burials that were heavily disturbed by modern construction are excluded to avoid misinterpreting from incomplete data. Since the accumulation of imported prestige goods in burials is commonly observed, we assign the burials into four classes, high, medium, low, and none, according to the total number of burial goods as an index of wealth.

@@

Based on the quantity of grave goods among burials, we can reconstruct social networks from the distribution of prestige goods, including imported ceramic and beads based on the principle that prestige materials usually relate to social status. We build network where burials represent actors (nodes in the network) linked by sharing the same prestige goods.

We assume burial network represents the relations among people and social structure based on the argument that

## Bayesian inference for Exponential Random Graph Models
